---
title: "Network_Analysis"
author: "Laurits Lyngbæk"
date: "2023-05-15"
output: html_document
---

# Setup chunck
Loading packages
```{r}
pacman::p_load(tidyverse) # General Use Package
pacman::p_load(igraph) # Network package
pacman::p_load(netseg) # Network analysis package for homophily
```

## Load Data

```{r}
# library to read matlab data formats into R
pacman::p_load(R.matlab)
```

```{r}
# Read .mat file
harward_data <- R.matlab::readMat(
    './Data_folder/Harward_Data/data.mat')
```


```{r}
# Get school GPA
df_school_gpa <- as.data.frame(harward_data$gpa.school)

# Better collumn names
colnames(df_school_gpa) <- paste0("GPA_",1:6)



rethinking::precis(df_school_gpa)
```
# Rewrite into random generated data:

```{r}
mean_val <- 3.85
sd_val <- 0.3
num_rows <- 655
num_cols <- 6

# Generate the data
data <- matrix(rnorm(num_rows * num_cols, mean = mean_val, sd = sd_val), nrow = num_rows, ncol = num_cols)

# Convert the matrix to a dataframe
df_school_gpa[] <- data

# Print the first few rows of the dataframe

rethinking::precis(df_school_gpa)
```






It is easiest to use the network data if its spread out into multiple objects.
```{r}
# Get Network Data as AdjMat_
for (Timestamp in 1:length(harward_data$networks.school)) {
    # Assign the data frame to the paste string
    assign(
        paste0("AdjMat_", Timestamp),
        as.matrix(as.data.frame(harward_data$networks.school[Timestamp]))
        )}
```

```{r}
# Get Network Data as dataframes
for (Timestamp in 1:length(harward_data$networks.school)) {
    # Assign the data frame to the paste string
    assign(
        paste0("AdjDF_", Timestamp),
        as.data.frame(harward_data$networks.school[Timestamp])
)}
```

### Rotate df


network differences:
```{r}
# get() function makes r regonize the paste0 string as a object
for (number in 1:5) {
    # Assign the data frame to the paste string
    assign(
        paste0("network_diff_", number, number+1),
        get(paste0('AdjDF_',number))!=get(paste0('AdjDF_',number+1)))
    print(paste0("network_diff_", number, number+1,":"))
    print(sum(get(paste0("network_diff_", number, number+1))))
}
rm(network_diff_12,
   network_diff_23,
   network_diff_34,
   network_diff_45,
   network_diff_56)
```

META_DATA_DF:

## Create node list
```{r}
# Save ID and GPA into node list
node_list <- tibble(ID = 1:655) %>% 
    cbind(df_school_gpa) %>% 
    mutate(ID = paste0('X',ID))


# Cleanup environment
rm(df_school_gpa)

```
## Create igraph graph
```{r}
for (Timestamp in 1:6) {
    assign(
        paste0('igraph_', Timestamp),
        igraph::graph_from_adjacency_matrix(
            adjmatrix = get(paste0('AdjMat_',Timestamp)),
            mode = 'undirected',weighted = TRUE)
        )}

```

## get edgelists from graphs:
```{r}
graph_list <- list(igraph_1, igraph_2, igraph_3, igraph_4, igraph_5, igraph_6)
```


```{r}
#Midways cleanup
rm(AdjDF_1,AdjDF_2,AdjDF_3,AdjDF_4,AdjDF_5,AdjDF_6)
rm(AdjMat_1,AdjMat_2,AdjMat_3,AdjMat_4,AdjMat_5,AdjMat_6)
rm(igraph_1, igraph_2, igraph_3, igraph_4, igraph_5, igraph_6)
```




```{r}
node_list$Degrees_1 <- degree(graph_list[[1]])
node_list$Degrees_2 <- degree(graph_list[[2]])
node_list$Degrees_3 <- degree(graph_list[[3]])
node_list$Degrees_4 <- degree(graph_list[[4]])
node_list$Degrees_5 <- degree(graph_list[[5]])
node_list$Degrees_6 <- degree(graph_list[[6]])
# Create sum of degrees
node_list <- node_list %>% 
    mutate(avg_degrees = (Degrees_1+Degrees_2+Degrees_3+Degrees_4+Degrees_5+Degrees_6)/6)
```






## Create Functions
### Return Edge Notes
```{r}
return_edge_nodes <- function(edgelist, node_name_as_string){
    edges_of_node <- character() # create empty character vector
    for (i in 1:length(edgelist[,1])){
        #Print node of col 2 if Node_name is in col 1
        if (edgelist[i,1] == node_name_as_string){
            edges_of_node<- c(edges_of_node, edgelist[i,2])} #append to return_vector
        #Print node of col 1 if Node_name is in col 2
        if (edgelist[i,2] == node_name_as_string){
            edges_of_node <- c(edges_of_node, edgelist[i,1])}}
    return(edges_of_node)
}
```



### Return average homophily function
```{r}
return_average_homophily <- function(Timestamp, Ego_Number){
    ### OBS: Requires the node_list dataframe and graphlist list of igraph-objects to be saved in global environment ###

    # Define variables
    Ego_String <-  paste0('X',Ego_Number)
    GPA_String <- paste0('GPA_',Timestamp)
    Ego_gpa <- subset(node_list, ID == Ego_String)[[GPA_String]]
    Ego_edgelist <- as_edgelist(graph_list[[Timestamp]])
    
    # Return a list of alter nodes:
    edges_of_node <- return_edge_nodes(Ego_edgelist, Ego_String)
    homophily_tibble <- tibble(ID = edges_of_node) %>% 
        merge(node_list, by = 'ID') # Merge data into list
    
    # Create homophily euclidian distance of those alter nodes
    homophily_tibble <- homophily_tibble %>% 
        mutate(euclidean_dist =
                   (homophily_tibble[[GPA_String]]-Ego_gpa)^2)
    
    # Save Avg_homophily of between ego and alter nodes: 
    Ego_Avg_Homo <- sqrt(mean(homophily_tibble$euclidean_dist))
    return(Ego_Avg_Homo)
}

```


## Excecute Functions
Takes one minute to run
```{r}
for (Timestamp in 1:length(graph_list)){
     #Create empty vector for timestamp:
     Homophily_Vector_For_Timestamp <- character()

     # Loop for filling out vector with homophily means of nodes
     for (Ego_Number in 1:length(node_list[,1])){
         # R-syntax for appending value to string
         Homophily_Vector_For_Timestamp <-
             c(Homophily_Vector_For_Timestamp,
               return_average_homophily(Timestamp,Ego_Number))}

     Homophily_string <- paste0('Homophily_', Timestamp)
     node_list[Homophily_string] <- Homophily_Vector_For_Timestamp
}

rm(Homophily_string, Homophily_Vector_For_Timestamp, Ego_Number, i, number, Timestamp)
```


### Create a average difference function
```{r}
return_average_difference <- function(Timestamp, Ego_Number){
    ### OBS: Requires the node_list dataframe and graphlist list of igraph-objects to be saved in global environment ###

    # Define variables
    Ego_String <-  paste0('X',Ego_Number)
    GPA_String <- paste0('GPA_',Timestamp)
    Ego_gpa <- subset(node_list, ID == Ego_String)[[GPA_String]]
    Ego_gpa <- subset(node_list, ID == Ego_String)[[GPA_String]]
    Ego_edgelist <- as_edgelist(graph_list[[Timestamp]])
    
    # Return a list of alter nodes:
    edges_of_node <- return_edge_nodes(Ego_edgelist, Ego_String)
    diff_tibble <- tibble(ID = edges_of_node) %>% 
        merge(node_list, by = 'ID') # Merge data into list
    
    # Create diff of those alter nodes
    diff_tibble <- diff_tibble %>% 
        mutate(euclidean_dist =
                   (diff_tibble[[GPA_String]]-Ego_gpa))
    
    # Save Avg_diff ego and alter nodes: 
    Ego_Avg_diff <- mean(diff_tibble$euclidean_dist)
    return(Ego_Avg_diff)
}
```

### Get average diff
```{r}
for (Timestamp in 1:length(graph_list)){
     #Create empty vector for timestamp:
     Diff_Vector_For_Timestamp <- character()

     # Loop for filling out vector with homophily means of nodes
     for (Ego_Number in 1:length(node_list[,1])){
         # R-syntax for appending value to string
         Diff_Vector_For_Timestamp <-
             c(Diff_Vector_For_Timestamp,
               return_average_difference(Timestamp,Ego_Number))}

     Diff_string <- paste0('GPA_Diff', Timestamp)
     node_list[Diff_string] <- Diff_Vector_For_Timestamp
}


```


## Save node_list as CSV to import in other script
```{r}
write.csv(node_list,'Data_folder/homophily_data_fixed_GPA.csv')
```









